---
title: "GPstat! (DailyMeasure)"
author: "David Fong"
date: "`r Sys.Date()`"
abstract: "Installation and configuration of **GPstat!**, a screening, preventative health activity, chronic disease management, care planning and billing aid for the **Best Practice** Electronic Medical Record."
output:
  html_document:
    number_sections: yes
    theme: lumen
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
  rmarkdown::html_vignette: null
vignette: >
  %\VignetteIndexEntry{DailyMeasure}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DailyMeasure)
```

# Video documentation

* <a href = "https://youtu.be/i6jhy_wY0bM" target = "_blank">Installation and basic configuration, including Best Practice server description</a>

* <a href = "https://youtu.be/4zuYG4uU4-4" target = "_blank">Demonstration of GPstat! features</a>

# Installation

* Run ('double-click') **GPstat! Setup**
* Choose Install Mode
  * **Install for me only** is recommended. GPstat! can then only be used by the current logged-in user.
* Choose installation directory
  * Clicking **Next** is recommended.
  * If *Install for me only*, this will be the a *Appdata\Local* directory
* 'Ready to Install' - Click **Install**
* Installation takes a few minutes
* 'Completing the GPstat! Setup Wizard' - Click **Finish**

# Configuration

## Setting the location of Best Practice database

* Choose **Configuration** from left-hand side-bar.
* Choose **Microsoft SQL Server details** tab from Configuration panel.

* If a server has already been configured, then choose with **Choose Best Practice Server** drop-down.

* If a server has not been configured, a new server description can be configured with the **New** button under *Server descriptions*
  * Choose a **Name** for the server description e.g. "Main", "MyServer", "MyClinic", ...
  * Enter the address of the server.
    * This will be of the form **CLINICSERVER\\BPSINSTANCE**
    * The address *CLINICSERVER* can be found in Best Practice through the *Setup-Configuration-Database* menu. Click **Find servers**, which will show the available Best Practice servers (usually just one!). Add '\\BPSINSTANCE' to the end of the server name.
  * Enter the database to be used. This will usually be **BPSPatients**. The other option is **BPSSamples**, which is the samples database.
  * Enter the UserID to be used. This will always be **bpsrawdata**
  * Enter the (database) Password. This is configured through the *Setup-Configuration-Database* menu in Best Practice. You may need to ask your system administrator what the database password is.
  * Click **Save**
  * Choose your new server description with the **Choose Best Practice server** dropdown. Messages should appear on the bottom-left of the screen indicating the success (or failure) of the server description configuration.

## Choosing configuration file

A configuration file, e.g. created by another user and available for system-wide use, can be chosen from the configuration panel.

* Choose **Configuration** from left-hand side-bar.
* Choose **Configuration file** tab.
* Click **Choose configuration file**, then choose the configuration file location.
* It is recommended that *GPstat!* is exited and re-started after choosing a configuration file.
  * To exit *GPstat!*, close the *GPstat!* window by clicking the cross on the top-right of the *GPstat!* window.
