---
title: "GPstat! user manual"
author: "David Fong"
date: "2nd December 2020"
output:
  rmdformats::readthedown:
    toc_depth: '4'
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: '4'
  html_document:
    toc: yes
    toc_depth: '4'
    df_print: paged
geometry: margin=25mm
fontsize: 12pt
documentclass: article
classoption: a4paper
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pipeR)

# user manual compiled through rintrojs walkthroughs
```

# Introduction

User documentation for [GPstat!](https://github.com/DavidPatShuiFong/DailyMeasure).

For video demonstrations, configuration and technical information, please refer to
the [DailyMeasure github page](https://github.com/DavidPatShuiFong/DailyMeasure).

The documentation seen here is also available when using the GPstat! software, look for the
academic hat near the top-left corner!

# GPstat! overview - the left sidebar

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_overview_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

# Basic functionality

## Choosing patient appointment, or contact, lists (right sidebar)

### Choosing clinicians and dates

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_choose_clinician_date_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### Choose contact type

For 'contact view' or 'PIP quality improvement'. *Not* for appointment  view.

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_choose_contact_details_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## The central view - Patient list display

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_datatable_helpers(NA) %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

# Views

## Appointments view

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_appointment_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Immunization view

```{r echo=FALSE}
htmltools::HTML(paste(DailyMeasure::steps_immunization_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Cancer screen view

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(DailyMeasure::steps_cancerscreen_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Conditions view

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(DailyMeasure::steps_conditions_df() %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Chronic Disease Management view

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureCDM::steps_introduction_df(as.character(NA)) %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Billing view

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureBillings::steps_introduction_df(as.character(NA)) %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

## Quality Improvement Measures (QIM)

### 'Active' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "Active") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### 'Diabetes' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "Diabetes") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### 'Cervical Screening' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "Cervical Screening") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### '15+' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "15+") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### '65+' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "65+") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### 'COPD (Lung Disease)' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "COPD (Lung Disease)") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```

### 'Cardiovascular risk' tab

```{r echo=FALSE, results='asis'}
htmltools::HTML(paste(dMeasureQIM::steps_introduction_df(as.character(NA), "Cardiovascular risk") %>>%
                        dplyr::pull("intro"),
                      collapse = "<br><br>"))
```
